Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-06 tex/VHzQ.tex
light_curves/MIR_LCs big update

For the 362 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).  For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands). These values are directly from the {\tt w$x$cov} entries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.

>>>>

%% For the 362 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).  For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands). These values are directly from the {\tt w$x$cov} entries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.
